\chapter*{Ethical Considerations}

As with any piece of work, there exists the potential for the work to be used with malicious intentions which were not the intentions of the authors.
The efforts of improving visual speech recognition allow for the attainment of conversations between individuals who may be believed to be engaging in private discussion.
The scenario in which lip reading accuracy reached a high reduction accuracy and the tools for making such predictions become accessible to both the public and commercial entities, an environment in which you can be seen but not heard may no longer exist.
This could be widely considered a breach of Article 8 of the European Convention on Human Rights \cite{EuropeanConventiononHumanRights} by undertaking ``intrusive surveillance'' against an individual.

The models developed in this report however currently require full head scans requiring a multiple camera set-up, followed by considerable processing to construct the facial meshes.
However, the principals investigated here could be implemented with a single depth camera, although the quality of the results cannot be commented on without further work.
Due to the symmetrical nature of faces, it may be found that a capture from a single side of a face may allow for the inference of the unseen face, enabling Blendshape Parameters to be estimated and speech predicted from this.
While the public availability of these cameras becomes more widespread, this may pose a greater threat to the public.

\begin{longtable}{ p{.80\textwidth} | c | c }
         & Yes & No \\ \hline
        \textbf{Section 1: HUMAN EMBRYOS/FOETUSES} & &  \\ \hline
        Does your project involve Human Embryonic Stem Cells? & & \checkmark \  \\ \hline
        Does your project involve the use of human embryos? & & \checkmark \  \\ \hline
        Does your project involve the use of human foetal tissues / cells? & & \checkmark \  \\ \hline
        \textbf{Section 2: HUMANS} & \  & \  \\ \hline
        Does your project involve human participants? & & \checkmark \  \\ \hline
        \textbf{Section 3: HUMAN CELLS / TISSUES} & \  & \  \\ \hline
        Does your project involve human cells or tissues? (Other than from ``Human Embryos/Foetuses'' i.e. Section 1)? & & \checkmark \  \\ \hline
        \textbf{Section 4: PROTECTION OF PERSONAL DATA} & \  & \  \\ \hline
        Does your project involve personal data collection and/or processing? & & \checkmark \  \\ \hline
        Does it involve the collection and/or processing of sensitive personal data (e.g. health, sexual lifestyle, ethnicity, political opinion, religious or philosophical conviction)? & & \checkmark \  \\ \hline
        Does it involve processing of genetic information? & & \checkmark \  \\ \hline
        Does it involve tracking or observation of participants? It should be noted that this issue is not limited to surveillance or localization data. It also applies to Wan data such as IP address, MACs, cookies etc. & & \checkmark \  \\ \hline
        Does your project involve further processing of previously collected personal data (secondary use)? For example Does your project involve merging existing data sets? & & \checkmark \  \\ \hline
        \textbf{Section 5: ANIMALS} & \  & \  \\ \hline
        Does your project involve animals? & & \checkmark \  \\ \hline
        \textbf{Section 6: DEVELOPING COUNTRIES} & \  & \  \\ \hline
        Does your project involve developing countries? & & \checkmark \  \\ \hline
        If your project involves low and/or lower-middle income countries, are any benefit-sharing actions planned? & & \checkmark \  \\ \hline
        Could the situation in the country put the individuals taking part in the project at risk? & & \checkmark \  \\ \hline
        \textbf{Section 7: ENVIRONMENTAL PROTECTION AND SAFETY} & \  & \  \\ \hline
        Does your project involve the use of elements that may cause harm to the environment, animals or plants? & & \checkmark \  \\ \hline
        Does your project deal with endangered fauna and/or flora /protected areas? & & \checkmark \  \\ \hline
        Does your project involve the use of elements that may cause harm to humans, including project staff? & & \checkmark \  \\ \hline
        Does your project involve other harmful materials or equipment, e.g. high-powered laser systems? & & \checkmark \  \\ \hline
        \textbf{Section 8: DUAL USE} & \  & \  \\ \hline
        Does your project have the potential for military applications? & & \checkmark \  \\ \hline
        Does your project have an exclusive civilian application focus? & & \checkmark \  \\ \hline
        Will your project use or produce goods or information that will require export licenses in accordance with legislation on dual use items? & & \checkmark \  \\ \hline
        Does your project affect current standards in military ethics e.g., global ban on weapons of mass destruction, issues of proportionality, discrimination of combatants and accountability in drone and autonomous robotics developments, incendiary or laser weapons? & & \checkmark \  \\ \hline
        \textbf{Section 9: MISUSE} & \  & \  \\ \hline
        Does your project have the potential for malevolent / criminal / terrorist abuse? & \checkmark & \  \\ \hline
        Does your project involve information on/or the use of biological, chemical, nuclear/radiological-security sensitive materials and explosives, and means of their delivery? & & \checkmark \  \\ \hline
        Does your project involve the development of technologies or the creation of information that could have severe negative impacts on human rights standards (e.g. privacy, stigmatization, discrimination), if misapplied? & & \checkmark \  \\ \hline
        Does your project have the potential for terrorist or criminal abuse e.g. infrastructural vulnerability studies, cybersecurity related project? & & \checkmark \  \\ \hline
        \textbf{SECTION 10: LEGAL ISSUES} & \  & \  \\ \hline
        Will your project use or produce software for which there are copyright licensing implications? & & \checkmark \  \\ \hline
        Will your project use or produce goods or information for which there are data protection, or other legal implications? & & \checkmark \  \\ \hline
        \textbf{SECTION 11: OTHER ETHICS ISSUES} & \  & \  \\ \hline
        Are there any other ethics issues that should be taken into consideration? & & \checkmark \  \\ 
\end{longtable} 
    