%\documentclass[12pt]{report}
\documentclass[12pt,a4paper,twoside]{report}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Definitions for the title page

\newcommand{\reporttitle}{Lip Reading in 3D}
\newcommand{\reportauthor}{Peter Robertson}
\newcommand{\supervisor}{Dr Stefanos Zafeiriou}
\newcommand{\degreetype}{Computing Science / Machine Learning}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% load some definitions and default packages
\input{includes}

% load some macros
\input{notation}

\date{September 2019}

\begin{document}

% load title page
\input{titlepage}


% page numbering etc.
\pagenumbering{roman}
\clearpage{\pagestyle{empty}\cleardoublepage}
\setcounter{page}{1}
\pagestyle{fancy}

\fancyhf{}
\fancyfoot[C]{\thepage}
\fancyhead[RE]{\nouppercase{\leftmark}}
\fancyhead[LO]{\nouppercase{\rightmark}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Lip reading is a skill which is renowned for being challenging for humans, with few individuals being capable of implementing the skill successfully.
Recent successes have been made in training Machine Learning models to predict speech from video inputs which have been able to outperform human level accuracy.
Currently however, no models exist which have attempted to use 3D data of facial scans for the use of lip reading.
In this report lip reading is successfully implemented with the use of 3D facial scans to make predictions on a word level with above 50\% mean test accuracy on 500 labels, forming the baseline for future work to build upon.
The current lack of datasets suitable for this research is the dominant problem in this field of research.
In addition to the task of lip reading from 3D facial scans, solving this secondary problem is also attempted.
As a means to help resolve this issue, the use of Generative Adversarial Networks is investigated as a means of generating 3D facial data corresponding to an audio input.
\end{abstract}

\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
I would like to thank the support of my supervisor; Dr Stefanos Zafeiriou, for his words of advice and guidance in this project.

Secondly I would like to thank the researchers for assisting with support, resources and advice; Athanasios Papaioannou, Evangelos Ververas and Panagiotis Tzirakis.

\clearpage{\pagestyle{empty}\cleardoublepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%--- table of contents
%\fancyhead[R,LO]{\sffamily {Table of Contents}}
\tableofcontents 
\listoffigures
\listoftables


\clearpage{\pagestyle{empty}\cleardoublepage}
\pagenumbering{arabic}
\setcounter{page}{1}
%\lhead[<even output>]{<odd output>}
%\rhead[<even output>]{<odd output>}
%\fancyhead[L,RO]{\slshape \rightmark}
%\fancyhead[LE,R]{\slshape \leftmark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\linenumbers
\input{introduction.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{facial_modelling_background.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{deep_learning_background.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{lit_review}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{blendshape_classification}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{generation}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{conclusions}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{ethics}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{appendix}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% bibliography
\newpage
\bibliographystyle{unsrt}
\bibliography{ref}


\end{document}
